Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-13 Paper/paper.tex
Updated figures in results section, added explanation for country choices

\newcommand{\toolname}{BGP-SAS }
\newcommand{\Ben}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommand{\Steph}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}

@@

% Chokepoint Evolution
There is ongoing research interest into ASes that intercept large portions of Internet paths \cite{throats}, \cite{decoy}. Some questions remain unanswered however. For instance, to what
extent does the current state of the Internet support national governments' attempts to censor Internet traffic? How does this vary from nation to nation? Is the Internet developing more
powerful chokepoints, or becoming more evenly accessible?
\par
To probe these questions we first used our chokepoint evaluation technique to investigate the chokepoint potential of all nations for the current Internet as well as the
change in chokepoint potentials over time. We looked at multiple snapshots of AS relationships from the CAIDA dataset (2012-2018).
For each timestamp, we generated routing trees based on these relationships. Then we calculated the chokepoint potential for every border node per snapshot. As a result we can investigate
how countries have changed overtime in their capability to enact censorship and surveillance. This is an attempt to understand what topological trends have developed historically.
With this test we can compare nations, and see which ones have overtime increased their capability to control the flow of information across their borders.

% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can easily implement censorship, it stands to reason that their might already be a negative relationship between
the chokepoint potential of a nation and its Internet freedom. If a significant relationship were to be found it would strengthen chokepoint potential as a measure of a nation's censorship capability
and it would increase the value in monitoring chokepoint potentials across the globe.
\par
We tested whether a significant relationship exists between our measure of national chokepoints and a qualitative evaluation of Internet Freedom. For Internet Freedom we used
the Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries. Each country receives a numerical score from 0 (the most free)
to 100 (the least free).
 To evaluate our measure, we first must define a way to rank each nation in regards to our chokepoint potential measure.
Acharya et al. \cite{throats} chose to determine how many ASes were needed (globally) to intercept 90\% of paths as a measure of the AS hierarchy. We choose a similar measure. Because we are
looking at national comparisons, however, we record how many border ASes are required to incercept 90\% of in-to-out or out-to-in paths for each nation. We compared this number
with each nation's (of those recorded by Freedom House) freedom on the net score.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_CN}
	\caption{The evolution of China's in-to-out Chokepoint Potential}\label{fig:ChinaChokePoint}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_US}
	\caption{The evolution of the US's Chokepoint Potential}\label{fig:USChokePoint}
\end{figure}

To inspect the changes over time for each nation we arrange all the border nodes belonging to a nation into a list. The list of border ASes is reverse sorted
so that the first AS has the highest chokepoint potential. The sum of all these nodes' chokepoint potential is 1.0. Then we step through the list, and record
the cumulative chokepoint potential of all the ASes seen so far. If we plot the number of ASes controled vs the cumulative chokepoint potential for that number
of ASes, we can see how many ASes are required for a certain nation to control different percentages of paths. We repeat this process for each snapshot to highlight
changes over time.

\par
For instance, consider figures \ref{fig:ChinaChokePoint} and \ref{fig:USChokePoint}. 
The x-axis (log-scale, so that countries with large differences in AS counts can be compared more easily)
is the number of border nodes controlled, and the y-axis is the ratio of in-to-out paths intercepted. Each line represents a different snapshot, with the more red lines being
farther in the past and more blue lines being more recent.

\par
The United States and China are shown here to exhibit their dramatic differences. First, it is worth pointing out that the United States has many more ASes than China, hence
it's line extends further to the right in these plots. We also see that China, in all cases, can control a much larger portion of its paths with much fewer ASes than the
United States. This result is entirely expected. Of more interest is the trends that can be seen over time. China clearly has developed an AS topology such that very few
ASes can intercept nearly all BGP paths. The US has evolved in a different way. While it has become somewhat easier for the US to intercept most of its paths, it has become
more difficult to intercept around 70\% of its paths and higher. This suggest an expansion of ASes on the interior and more connections, as well as a strengthening of
the very top ASes.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{single_DE}
	\caption{The evolution of Germany's in-to-out Chokepoint Potential}\label{fig:GermChokePoint}
\end{figure}

\par
Not all nations have evolved to a state where it easier to control paths. One example is Germany, as shown in figure \ref{fig:GermChokePoint}. For Germany, a fairly constant
trend shows that it has become more difficult to intercept BGP paths. Unlike the other examples, any amount of German border ASes intercept less paths in more recent tests.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesNeeded}
	\caption{Number of ASes to intercept 90\% of ito paths for multiple nations over time}\label{fig:nodes}
\end{figure}

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in figure \ref{fig:nodes}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Iran) as well as the increase for other nations
(Germany and Brazil). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.

>>>>

\newcommand{\toolname}{BGP-SAS }
\newcommand{\timerange}{(2012-2018)}

\newcommand{\Ben}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommand{\Steph}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}

@@

% Chokepoint Evolution
There is ongoing research interest into ASes that intercept large portions of Internet paths \cite{throats}, \cite{decoy}. Some important questions remain unanswered however. For instance, to what
extent does the current state of the Internet support national governments' attempts to censor Internet traffic? How does this vary from nation to nation? Is the Internet developing more
powerful chokepoints, or becoming more evenly accessible?
\par
To probe these questions we first used our chokepoint evaluation technique to investigate the chokepoint potential of all nations for the current Internet as well as the
change in chokepoint potentials over time. We looked at multiple snapshots of AS relationships from the CAIDA dataset (2012-2018).
For each timestamp, we generated routing trees based on these relationships. Then we calculated the chokepoint potential for every border node per snapshot. As a result we can investigate
how countries have changed overtime in their capability to enact censorship and surveillance. This is an attempt to understand what topological trends have developed historically.
With this test we can compare nations, and see which ones have overtime increased their capability to control the flow of information across their borders.
\par
% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can easily implement censorship, it stands to reason that their might already be a negative relationship between
the chokepoint potential of a nation and its Internet freedom. If a significant relationship were to be found it would strengthen chokepoint potential as a measure of a nation's censorship capability
and it would increase the value in monitoring chokepoint potentials across the globe.
\par
We tested whether a significant relationship exists between our measure of national chokepoints and a qualitative evaluation of Internet Freedom. For Internet Freedom we used
the Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries. Each country receives a numerical score from 0 (the most free)
to 100 (the least free).
 To evaluate our measure, we first must define a way to rank each nation in regards to our chokepoint potential measure.
Acharya et al. \cite{throats} chose to determine how many ASes were needed (globally) to intercept 90\% of paths as a measure of the AS hierarchy. We choose a similar measure. Because we are
looking at national comparisons, however, we record how many border ASes are required to incercept 90\% of in-to-out or out-to-in paths for each nation. We compared this number
with each nation's (of those recorded by Freedom House) freedom on the net score.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesFree}
	\caption{The number of border ASes required for the US, France, Germany, and Great Britain to intercept 90\% of in-to-out paths over time.}\label{fig:nodesFree}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesCensor}
	\caption{The number of border ASes required for Russia, Egypt, Turkey, and China to intercept 90\% of in-to-out paths over time.}\label{fig:nodesCensor}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{multi}
	\caption{The capability for various nations to intercept in-to-out paths over multiple years \timerange. Each plot shows for a number of border ASes controlled (x-axis),
	what fraction of in-to-out paths are intercepted (y-axis). Years in blue are more recent, and years in red are further in the past.}\label{fig:multiTime}
\end{figure*}

We have chosen to detail the results of our experiment for 8 nations due to their histories of censorship practice. First we have chosen 4 nations known to enact
extensive Internet censorship policies. These nations are China, Turkey, Egypt, and Russia. China has historically been the number one nation in regards to Internet
censorship \cite{censorshipSurvey}. Turkey has recently dramatically increased its online censorship efforts, by blocking social media accesses during turmoil and pressuring ISPs
to block access to material chosen by the Turkish government \cite{turkeyCensor}. The Internet of Egypt suffered severe shutdowns during the Arab Spring of the early 2010s \cite{arabspring}.
The Russian government has passed surveillance laws requiring ISPs to allow the Russian government access to user statistics \cite{censorshipGeography}. Next we have chosen the nations
of Germany, the United States, France, and the United Kingdom because, while they have all conducted limited forms of Internet censorship \cite{censorshipSurvey}, Internet access for these 
nations is considered highly open.

\par
To inspect the changes over time for each nation we arrange all the border nodes belonging to a nation into a list. The list of border ASes is reverse sorted
so that the first AS has the highest chokepoint potential. The sum of all these nodes' chokepoint potential is 1.0. Then we step through the list, and record
the cumulative chokepoint potential of all the ASes seen so far. If we plot the number of ASes controled vs the cumulative chokepoint potential for that number
of ASes, we can see how many ASes are required for a certain nation to control different percentages of paths. We repeat this process for each snapshot to highlight
changes over time.

\par
For instance, consider \figurename \ref{fig:multiTime}. 
The x-axis (log-scale, so that countries with large differences in AS counts can be compared more easily) for each plot
is the number of border nodes controlled, and the y-axis is the ratio of in-to-out paths intercepted. Each line represents a different snapshot, with the more red lines being
farther in the past and more blue lines being more recent.

\par
The United States and China are shown here and exhibit some dramatic differences. First, it is worth pointing out that the United States has many more ASes than China, hence
it's line extends further to the right in these plots. We also see that China, in all cases, can control a much larger portion of its paths with much fewer ASes than the
United States. This result is entirely expected. Of more interest is the trends that can be seen over time. The AS-level topology of China's Internet has evolved such that very few
ASes can intercept nearly all BGP paths. The US has evolved in a different way. While it has become somewhat easier for the US to intercept most of its paths, it has become
more difficult to intercept around 70\% of its paths and higher. This suggest an expansion of ASes on the interior and more connections, as well as a strengthening of
the very top ASes.

\par
Not all nations have evolved to a state where it easier to control paths. One example is Germany, as shown in \figurename \ref{fig:multiTime}. For Germany, a fairly constant
trend shows that it has become more difficult to intercept BGP paths. Unlike the other examples, any amount of German border ASes intercept less paths in more recent tests.

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in \figurename \ref{fig:nodesFree} and \figurename \ref{fig:nodesCensor}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Iran) as well as the increase for other nations
(Germany and France). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.
